regression analysis

### 2024-03-24 src/analysis/regression_analysis.Rmd
moved shiny app and changed data path regression_analysis

```{r saving the doc}
render("../../src/analysis/regression_analysis.Rmd",
       output_format = "pdf_document",
       "../../gen/data_analysis/regression_analysis.pdf")
```

>>>>

```{r saving the doc}
write_csv(graph_data, "../../data/graph_data.csv")

render("../../src/analysis/regression_analysis.Rmd",
       output_format = "pdf_document",
       "../../gen/data_analysis/regression_analysis.pdf")
```
